[WIP] Church Bells are Not Ringing: Decrease in the Opposite-Sex and Same-Sex Couples Opting for Religous Marriage Ceremonies in England and Wales

### 2024-04-24 paper/paper.qmd
paper update
paper and references update

This paper takes data from the **Office for National Statistics in the United Kingdom** from the 2020 edition of the "Marriages in England and Wales" data set to examine if the presence of religion in legal marriage has declined over time in tandem with answering if the result is difference between same and opposite sex couples. The estimand of interest is the presence of religion in consolidating a legal marriage. To examine whether or not religion in marriage has declined, graphical analysis was conducted to visualize the annual data on marriage ceremony type between 1970 to 2020 for opposite-sex couples and 2016 to 2020 for same-sex couples. Summary statistics were also calculated to get a greater idea of the numerical significance of religion in this space.

@@

## Data Description
The data sets for same and opposite-sex couples were derived from the *Office for National Statistics in the United Kingdom* with the 2020 edition of the “Marriages in England and Wales” workbook as raw data. This data is collected at the time a marriage is registered as part of civil registration which is a legal requirement in completing a legally recognized marriage in England and Wales. Annual marriage statistics are available to the public approximately two years after the end of the reference year [@statsguide]. Notably, same-sex couples that are currently in a civil partnership can have it converted to a marriage but these numbers are not counted towards the marriage statistics of same-sex couples in the workbook.

>>>>

This paper takes data from the *Office for National Statistics in the United Kingdom* from the 2020 edition of the "Marriages in England and Wales" data set to examine if the presence of religion in legal marriage has declined over time in tandem with answering if the result is difference between same and opposite sex couples. The estimand of interest is the presence of religion in consolidating a legal marriage. To examine whether or not religion in marriage has declined, graphical analysis was conducted to visualize the annual data on marriage ceremony type between 1970 to 2020 for opposite-sex couples and 2016 to 2020 for same-sex couples. Summary statistics were also calculated to get a greater idea of the numerical significance of religion in this space.

@@

## Data Description
The data sets for same and opposite-sex couples were derived from the *Office for National Statistics in the United Kingdom* with the 2020 edition of the “Marriages in England and Wales” workbook as raw data. This data is collected at the time a marriage is registered as part of civil registration which is a legal requirement in completing a legally recognized marriage in England and Wales. Annual marriage statistics are available to the public approximately two years after the end of the reference year [@statsguide]. Notably, same-sex couples that are currently in a civil partnership can have it converted to a marriage but these numbers are not counted towards the marriage statistics of same-sex couples in the workbook. The data collected and used in this paper is used to measure the number of couples that opt for civil or religious marriage ceremonies on a yearly basis [@statsguide]. By measuring marriage ceremony trends, it can help measure or provide insight onto greater social attitudes towards religion.
